---
title: "Regression result"
author: "Hao Sun"
date: "4/15/2023"
output: html_document
---

### Preparation {-}

```{r echo = F}
# use OLS regression 

library(tidyverse)

regdat <- readRDS("/Users/sunhao/Documents/GitHub/ChinaAg/From Hao/data/dongbei/regdat.rds") %>% 
  mutate(ex_revenue = yield_lag * ex_price + subsidy_lag, 
         tcost = yield_lag * cost,
         rcratio = (yield_lag * ex_price + subsidy_lag)/(yield_lag * cost))
preddat <- readRDS("/Users/sunhao/Documents/GitHub/ChinaAg/From Hao/data/dongbei/preddat.rds") %>% 
  mutate(ex_revenue = yield_lag * ex_price + subsidy_lag,
         tcost = yield_lag * cost,
         rcratio = (yield_lag * ex_price + subsidy_lag)/(yield_lag * cost))

# true share: 
share_true <- preddat$share %>% matrix(., nrow = 4)


# add expected profit for each crop 
regdat <- regdat %>% 
  mutate(pfex_corn = regdat %>% filter(crop == "corn") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_rice = regdat %>% filter(crop == "rice") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_soy = regdat %>% filter(crop == "soybean") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_wheat = regdat %>% filter(crop == "wheat") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         revex_corn = regdat %>% filter(crop == "corn") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_rice = regdat %>% filter(crop == "rice") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         revex_soy = regdat %>% filter(crop == "soybean") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_wheat = regdat %>% filter(crop == "wheat") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_corn = regdat %>% filter(crop == "corn") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_rice = regdat %>% filter(crop == "rice") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_soy = regdat %>% filter(crop == "soybean") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_wheat = regdat %>% filter(crop == "wheat") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector())%>% 
  mutate(rr_corn = revex_corn/revex_wheat, 
         rr_rice = revex_rice/revex_wheat,
         rr_soy = revex_soy/revex_wheat,
         rc_corn = tcost_corn/tcost_wheat, 
         rc_rice = tcost_rice/tcost_wheat,
         rc_soy = tcost_soy/tcost_wheat)


# same for the predicted data 
preddat <- preddat %>% 
  mutate(pfex_corn = preddat %>% filter(crop == "corn") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_rice = preddat %>% filter(crop == "rice") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_soy = preddat %>% filter(crop == "soybean") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% #"+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_wheat = preddat %>% filter(crop == "wheat") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% #"+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         revex_corn = preddat %>% filter(crop == "corn") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_rice = preddat %>% filter(crop == "rice") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         revex_soy = preddat %>% filter(crop == "soybean") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_wheat = preddat %>% filter(crop == "wheat") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_corn = preddat %>% filter(crop == "corn") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_rice = preddat %>% filter(crop == "rice") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_soy = preddat %>% filter(crop == "soybean") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_wheat = preddat %>% filter(crop == "wheat") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector()) %>% 
  mutate(rr_corn = revex_corn/revex_wheat, 
         rr_rice = revex_rice/revex_wheat,
         rr_soy = revex_soy/revex_wheat,
         rc_corn = tcost_corn/tcost_wheat, 
         rc_rice = tcost_rice/tcost_wheat,
         rc_soy = tcost_soy/tcost_wheat)
```


The true share for all 6 provinces in 2021 are 

```{r}
share_true %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

The **expected profit** of crop $i$ in province $j$ and year $t$ is defined as 

$$
Ef_{ijt} =  \tilde{y}_{ijt} (p^*_{it} - c_{ijt} )+ \tilde{d}_{ijt}
$$

where: 

+ $p^*{it}$: averaged national expected price (yuan per kilogram) in March of the current year $t$
+ $c_{ijt}$: the current cost (yuan per kilogram) of crop $i$ in province $j$ and year $t$
+ $\tilde{y}_{ijt}$: the averaged yield (kilogram per mu) of crop $i$ in province $j$ in the past three years, $\{t-3, t-2, t-1\}$. 
+ $\tilde{d}_{ijt}$: the weighted average of subsidy (yuan per mu) of crop $i$ in province $j$ in the past two years, with $\tilde{d}_{ijt} = 0.67 * d_{ij,t-1} + 0.33 * d_{ij, t-2}$

The **true profit** of crop $i$ in province $j$ and year $t$ is defined as

$$
f_{ijt} = y_{ijt}(p_{ijt} - c_{ijt} )  + d_{ijt}
$$
where $p_{ijt}$ is the true province level crop price (yuan per kilogram) for crop $i$ in province $j$ and year $t$. 


The expected revenue of crop $i$ in province $j$ and year $t$ is 

$$
r_{ijt} =  \tilde{y}_{ijt} p^*_{it} + \tilde{d}_{ijt} = Ef_{ijt} + \tilde{y}_{ijt} c_{ijt}
$$

The relative revenus of crop $i$ in province $j$ and year $t$ is 

$$
rr_{ijt} = r_{ijt}/r_{4jt}
$$

### OLS regression {-}

Suppose $s_{ijt}$ is the share of cropland area for crop $i$ in province $j$ and year $t$. Let $s_{0jt} = 1 - \sum_{i=1}^4 s_{ijt}$. 

We define $z_{ijt} = \log(s_{ijt}/s_{0jt})$ as the response variable. 

#### Model 1 : Use expected profit {-}

$$
z_{ijt} = \beta_{i0} + \sum_{k=1}^4 Ef_{kjt}\beta_{ik}+ u_{j} + \epsilon_{ijt}
$$
where 

+ $u_j$: fixed effect for province $j$, assumed as time invariant. 
+ $\epsilon_{ijt}$: random error, assumed i.i.d. with normal distribution 


#### Model 2 : Use expected revenue {-}

$$
z_{ijt} = \beta_{i0} + \sum_{k=1}^4 r_{kjt}\beta_{ik}+ u_{j} + \epsilon_{ijt}
$$


#### Model 3: Use relative revenue {-}

$$
z_{ijt} = \beta_{i0} + \sum_{k=1}^3 rr_{kjt}\beta_{ik}+ u_{j} + \epsilon_{ijt}
$$
#### Some figures {-}

Expected profit against share for corn: 

```{r}
ggplot(aes(x = pfex_corn, y = share), data = regdat %>% filter(crop == "corn")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free_y")
```

Expected revenue against share for corn: 

```{r}
ggplot(aes(x = revex_corn, y = share), data = regdat %>% filter(crop == "corn")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free_y")
```

Logriathm of expected revenue against share for corn: 

```{r}
ggplot(aes(x = revex_corn, y = log(share)), data = regdat %>% filter(crop == "corn")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free_y")
```


Logriathm of expected revenue against share for rice: 

```{r}
ggplot(aes(x = revex_rice, y = log(share)), data = regdat %>% filter(crop == "rice")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free")
```

Logriathm of expected revenue against share for soybean: 

```{r}
ggplot(aes(x = revex_soy, y = log(share)), data = regdat %>% filter(crop == "soybean")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free")
```

Logriathm of expected revenue against share for soybean: 

```{r}
ggplot(aes(x = revex_wheat, y = log(share)), data = regdat %>% filter(crop == "wheat")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free")
```



#### Try the two basic models {-}

```{r}
lm_corn <- lm(y ~ 0 + pfex_corn + region,
              data = regdat %>% filter(crop == "corn"))
summary(lm_corn)
```


```{r}
lm_corn <- lm(y ~ 0 + revex_corn + region,
              data = regdat %>% filter(crop == "corn"))
summary(lm_corn)
```


#### Model 1 Regression {-}

```{r}
lm_corn_pf <- lm(y ~ 0 + pfex_corn + pfex_rice + pfex_soy + pfex_wheat + region,
              data = regdat %>% filter(crop == "corn"))

lm_rice_pf <- lm(y ~ 0 + pfex_corn + pfex_rice + pfex_soy + pfex_wheat + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_pf <- lm(y ~ 0 + pfex_corn + pfex_rice + pfex_soy + pfex_wheat + region,
              data = regdat %>% filter(crop == "soybean"))

lm_wheat_pf <- lm(y ~ 0 + pfex_corn + pfex_rice + pfex_soy + pfex_wheat + region,
              data = regdat %>% filter(crop == "wheat"))


summary(lm_corn_pf)
summary(lm_rice_pf)
summary(lm_soy_pf)
summary(lm_wheat_pf)
```


#### Model 2 Regression {-}

```{r}
lm_corn_rev <- lm(y ~ 0 + revex_corn + revex_rice + revex_soy + revex_wheat  + region,
              data = regdat %>% filter(crop == "corn"))

lm_rice_rev <- lm(y ~ 0 + revex_corn + revex_rice + revex_soy + revex_wheat + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_rev <- lm(y ~ 0 + revex_corn + revex_rice + revex_soy + revex_wheat  + region,
              data = regdat %>% filter(crop == "soybean"))

lm_wheat_rev <- lm(y ~ 0 + revex_corn + revex_rice + revex_soy + revex_wheat  + region,
              data = regdat %>% filter(crop == "wheat"))


summary(lm_corn_rev)
summary(lm_rice_rev)
summary(lm_soy_rev)
summary(lm_wheat_rev)
```

#### Model 3 Regression {-} 

```{r}
lm_corn_rr <- lm(y ~ 0 + rr_corn + rr_rice + rr_soy + region, # rc_corn + rc_rice + rc_soy + 
              data = regdat %>% filter(crop == "corn"))

lm_rice_rr <- lm(y ~ 0 + rr_corn + rr_rice + rr_soy + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_rr <- lm(y ~ 0 +  rr_corn + rr_rice + rr_soy +  region,
              data = regdat %>% filter(crop == "soybean"))

lm_wheat_rr <- lm(y ~ 0 +  rr_corn + rr_rice + rr_soy +  region,
              data = regdat %>% filter(crop == "wheat"))


summary(lm_corn_rr)
summary(lm_rice_rr)
summary(lm_soy_rr)
summary(lm_wheat_rr)
```


#### Prediction Results {-}

```{r echo = F}
pd_corn_pf <- predict(lm_corn_pf, newdata = preddat %>% filter(crop == "corn"))
pd_rice_pf <- predict(lm_rice_pf, newdata = preddat %>% filter(crop == "rice"))
pd_soy_pf <- predict(lm_soy_pf, newdata = preddat %>% filter(crop == "soybean"))
pd_wheat_pf <- predict(lm_wheat_pf, newdata = preddat %>% filter(crop == "wheat"))

y_pred_pf <- rbind(pd_corn_pf, pd_rice_pf, pd_soy_pf, pd_wheat_pf)

share_est_pf <- round(sweep(exp(y_pred_pf), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_pf)) + 1) * 100, 2)


pd_corn_rev <- predict(lm_corn_rev, newdata = preddat %>% filter(crop == "corn"))
pd_rice_rev <- predict(lm_rice_rev, newdata = preddat %>% filter(crop == "rice"))
pd_soy_rev <- predict(lm_soy_rev, newdata = preddat %>% filter(crop == "soybean"))
pd_wheat_rev <- predict(lm_wheat_rev, newdata = preddat %>% filter(crop == "wheat"))

y_pred_rev <- rbind(pd_corn_rev, pd_rice_rev, pd_soy_rev, pd_wheat_rev)

share_est_rev <- round(sweep(exp(y_pred_rev), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_rev)) + 1) * 100, 2)



pd_corn_rr<- predict(lm_corn_rr, newdata = preddat %>% filter(crop == "corn"))
pd_rice_rr <- predict(lm_rice_rr, newdata = preddat %>% filter(crop == "rice"))
pd_soy_rr <- predict(lm_soy_rr, newdata = preddat %>% filter(crop == "soybean"))
pd_wheat_rr <- predict(lm_wheat_rr, newdata = preddat %>% filter(crop == "wheat"))

y_pred_rr <- rbind(pd_corn_rr, pd_rice_rr, pd_soy_rr, pd_wheat_rr)

share_est_rr <- round(sweep(exp(y_pred_rr), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_rr)) + 1) * 100, 2)

```

True Result in 2021

```{r}
share_true %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

Model 1 Prediction

```{r}
share_est_pf %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

Model 2 Prediction

```{r}
share_est_rev %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

Model 3 Prediction

```{r}
share_est_rr %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

#### MSE Results {-}

```{r}
MSE1 <- rowMeans((share_true - share_est_pf)^2)
MSE2 <- rowMeans((share_true - share_est_rev)^2)
MSE3 <- rowMeans((share_true - share_est_rr)^2)

cbind(MSE1, MSE2, MSE3) %>% "colnames<-"(paste0("Model", 1:3)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

