---
title: "Regression Xiaolan 0418"
author: "Xiaolan"
date: "2023-04-20"
output:
  pdf_document: default
  html_document:
    df_print: paged
---



---
title: "Regression result April 15"
author: "Xiaolan"
date: "4/19/2023"
output:
  pdf_document: default
  html_document: default
---

### Preparation {-}

```{r echo = F, include=FALSE}
# use OLS regression 

library(tidyverse)
library(stargazer)

regdat <- readRDS("~/Documents/GitHub/ChinaAg/From Hao/data/dongbei/regdat.rds")  %>% 
  mutate(ex_revenue = yield_lag * ex_price + subsidy_lag, 
         tcost = yield_lag * cost,
         rcratio = (yield_lag * ex_price + subsidy_lag)/(yield_lag * cost)) %>% 
  filter(region == "Neimenggu"|region == "Heilongjiang"|region == "Jilin"|region =="Liaoning")

regdat <- regdat %>% 
  mutate(share_wheat = regdat %>% filter(crop == "wheat") %>% "$"(share) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector()) %>% 
  mutate(y2 = log(share/(other + share_wheat)))   # get new y2 since now we combine other and wheat

preddat <- readRDS("~/Documents/GitHub/ChinaAg/From Hao/data/dongbei/preddat.rds") %>% 
  mutate(ex_revenue = yield_lag * ex_price + subsidy_lag,
         tcost = yield_lag * cost,
         rcratio = (yield_lag * ex_price + subsidy_lag)/(yield_lag * cost)) %>% 
  filter(region == "Neimenggu"|region == "Heilongjiang"|region == "Jilin"|region =="Liaoning")

preddat <- preddat %>% 
  mutate(share_wheat = preddat %>% filter(crop == "wheat") %>% "$"(share) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector()) %>% 
  mutate(y2 = log(share/(other + share_wheat))) 


# true share: 
share_true <- preddat$share %>% matrix(., nrow = 4) %>% "["(-4,)



# add expected profit for each crop 
regdat <- regdat %>% 
  mutate(pfex_corn = regdat %>% filter(crop == "corn") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_rice = regdat %>% filter(crop == "rice") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_soy = regdat %>% filter(crop == "soybean") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_wheat = regdat %>% filter(crop == "wheat") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         
         pftr_corn = regdat %>% filter(crop == "corn") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pftr_rice = regdat %>% filter(crop == "rice") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pftr_soy = regdat %>% filter(crop == "soybean") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pftr_wheat = regdat %>% filter(crop == "wheat") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 20) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         
         revex_corn = regdat %>% filter(crop == "corn") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_rice = regdat %>% filter(crop == "rice") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         revex_soy = regdat %>% filter(crop == "soybean") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_wheat = regdat %>% filter(crop == "wheat") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         
         tcost_corn = regdat %>% filter(crop == "corn") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_rice = regdat %>% filter(crop == "rice") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_soy = regdat %>% filter(crop == "soybean") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_wheat = regdat %>% filter(crop == "wheat") %>% "$"(tcost) %>% 
           matrix(., nrow = 20) %>% 
           kronecker(rep(1, 4), .) %>% as.vector())%>% 
 mutate(rr_corn = revex_corn/revex_soy, 
         rr_rice = revex_rice/revex_soy,
         rc_corn = tcost_corn/tcost_soy, 
         rc_rice = tcost_rice/tcost_soy,
         rr_corn2 = revex_corn/revex_rice,
         rr_soy2 = revex_soy/revex_rice)


# same for the predicted data 
preddat <- preddat %>% 
  mutate(pfex_corn = preddat %>% filter(crop == "corn") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_rice = preddat %>% filter(crop == "rice") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_soy = preddat %>% filter(crop == "soybean") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% #"+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pfex_wheat = preddat %>% filter(crop == "wheat") %>% "$"(profit_ex) %>% 
           matrix(., nrow = 1) %>% #"+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         
         pftr_corn = preddat %>% filter(crop == "corn") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pftr_rice = preddat %>% filter(crop == "rice") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 1) %>% # "+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pftr_soy = preddat %>% filter(crop == "soybean") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 1) %>% #"+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         pftr_wheat = preddat %>% filter(crop == "wheat") %>% "$"(profit_true_lag) %>% 
           matrix(., nrow = 1) %>% #"+"(400) %>% log() %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         
         revex_corn = preddat %>% filter(crop == "corn") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_rice = preddat %>% filter(crop == "rice") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         revex_soy = preddat %>% filter(crop == "soybean") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         revex_wheat = preddat %>% filter(crop == "wheat") %>% "$"(ex_revenue) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_corn = preddat %>% filter(crop == "corn") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_rice = preddat %>% filter(crop == "rice") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(),
         tcost_soy = preddat %>% filter(crop == "soybean") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector(), 
         tcost_wheat = preddat %>% filter(crop == "wheat") %>% "$"(tcost) %>% 
           matrix(., nrow = 1) %>% 
           kronecker(rep(1, 4), .) %>% as.vector()) %>% 
  mutate(rr_corn = revex_corn/revex_soy, 
         rr_rice = revex_rice/revex_soy,
         rc_corn = tcost_corn/tcost_soy, 
         rc_rice = tcost_rice/tcost_soy,
         rr_corn2 = revex_corn/revex_rice,
         rr_soy2 = revex_soy/revex_rice)
```





```{r echo = F, include=FALSE}
#The true share for provinces in 2021 are 

share_true %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)) %>% pander::pander() 
```

The **expected profit** of crop $i$ in province $j$ and year $t$ is defined as 

$$
E\pi_{ijt} =  \tilde{y}_{ijt} (\tilde{p}_{it} - c_{ijt} )+ \tilde{d}_{ijt}
$$

where: 

+ $\tilde{p}_{it}$: future price (yuan per kilogram) averaged in March for Novermber delivery in year $t$
+ $c_{ijt}$: the realized cost (yuan per kilogram) of crop $i$ in province $j$ and year $t$
+ $\tilde{y}_{ijt}$: the yield (kilogram per mu) of crop $i$ in province $j$ averaged in the past three years, $\{t-3, t-2, t-1\}$. 
+ $\tilde{d}_{ijt}$: the expected subsidy (yuan per mu) of crop $i$ in province $j$ weighted for the past two years, with $\tilde{d}_{ijt} = 0.67 * d_{ij,t-1} + 0.33 * d_{ij, t-2}$

The **realized profit** of crop $i$ in province $j$ and year $t$ is defined as

$$
\pi_{ijt} = y_{ijt}(p_{ijt} - c_{ijt} )  + d_{ijt}
$$
where $p_{ijt}$ is the realized price (yuan per kilogram) for crop $i$ in province $j$ and year $t$. 


Thus, the expected revenue of crop $i$ in province $j$ and year $t$ is 

$$
Er_{ijt} =  \tilde{y}_{ijt} \tilde p_{it} + \tilde{d}_{ijt} = E\pi_{ijt} + \tilde{y}_{ijt} c_{ijt}
$$

We define the relative revenue of crop $i$ to a baseline crop wheat as:

$$
rr_{ijt} = r_{ijt}/r_{3jt}
$$

### OLS regression {-}

Suppose $s_{ijt}$ is the share of cropland area for crop $i$ in province $j$ and year $t$. Let $s_{0jt} = 1 - \sum_{i=1}^3 s_{ijt}$. 

We define $z_{ijt} = \log(s_{ijt}/s_{0jt})$ as the dependent variable. 

#### Model 1 : Use expected profit as explanatory variable {-}

$$
z_{ijt} = \beta_{i0} + \sum_{k=1}^3 E\pi_{kjt}\beta_{ik}+ u_{j} + \epsilon_{ijt}
$$
where 

+ $u_j$: fixed effect for province $j$. 
+ $\epsilon_{ijt}$: random error, assumed i.i.d. with normal distribution 


#### Model 2 : Use expected revenue {-}

$$
z_{ijt} = \beta_{i0} + \sum_{k=1}^3 Er_{kjt}\beta_{ik}+ u_{j} + \epsilon_{ijt}
$$


#### Model 3: Use expected relative revenue {-}

$$
z_{ijt} = \beta_{i0} + \sum_{k=1}^2 Err_{kjt}\beta_{ik}+ u_{j} + \epsilon_{ijt}
$$
Some figures: 

(1) Expected profit against acreage share for corn: 

```{r echo = F, include=FALSE}
ggplot(aes(x = pfex_corn, y = share), data = regdat %>% filter(crop == "corn")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free_y")+
  labs(x = "expected profit for corn", y = "acreage share")
```

(2) Expected revenue against acreage share: 

```{r echo = F, include=FALSE}
ggplot(aes(x = revex_corn, y = share), data = regdat %>% filter(crop == "corn")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free_y")+
  labs(x = "expected revenue for corn", y = "acreage share")
```

(3) Logriathm of expected revenue against acreage share: 

```{r echo = F, include=FALSE}
ggplot(aes(x = revex_corn, y = log(share)), data = regdat %>% filter(crop == "corn")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free_y")+
  labs(x = "Logriathm of expected revenue", y = "acreage share")
```




```{r echo=FALSE, include=FALSE}
## Logriathm of expected revenue against share for rice: 
ggplot(aes(x = revex_rice, y = log(share)), data = regdat %>% filter(crop == "rice")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free")

## Logriathm of expected revenue against share for soybean: 
ggplot(aes(x = revex_soy, y = log(share)), data = regdat %>% filter(crop == "soybean")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free")

## Logriathm of expected revenue against share for soybean: 
ggplot(aes(x = revex_wheat, y = log(share)), data = regdat %>% filter(crop == "wheat")) + geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~region, nrow = 2, scales = "free")
```




```{r echo=FALSE, include=FALSE}
#### Try the two basic models {-}
lm_corn <- lm(y ~ 0 + pfex_corn + region,
              data = regdat %>% filter(crop == "corn"))
summary(lm_corn)


lm_corn <- lm(y ~ 0 + revex_corn + region,
              data = regdat %>% filter(crop == "corn"))
summary(lm_corn)
```



#### Model 1 Regression {-}

```{r}
lm_corn_pf <- lm(y2 ~ 0 + pfex_corn + pfex_rice + pfex_soy  + region,
              data = regdat %>% filter(crop == "corn"))

lm_rice_pf <- lm(y2 ~ 0 + pfex_corn + pfex_rice + pfex_soy  + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_pf <- lm(y2 ~ 0 + pfex_corn + pfex_rice + pfex_soy  + region,
              data = regdat %>% filter(crop == "soybean"))


stargazer(lm_corn_pf, lm_rice_pf, lm_soy_pf, title = "Model 1 Results",column.labels = c("Corn", "Rice", "Soybean"), type = "text", digit = 3, dep.var.caption  = "")
```


#### Model 2 Regression {-}

```{r}
lm_corn_rev <- lm(y2 ~ 0 + revex_corn + revex_rice + revex_soy   + region,
              data = regdat %>% filter(crop == "corn"))

lm_rice_rev <- lm(y2 ~ 0 + revex_corn + revex_rice + revex_soy  + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_rev <- lm(y2 ~ 0 + revex_corn + revex_rice + revex_soy   + region,
              data = regdat %>% filter(crop == "soybean"))



stargazer(lm_corn_rev, lm_rice_rev, lm_soy_rev,  title = "Model 2 Results",column.labels = c("Corn", "Rice", "Soybean"), type = "text", digit = 3, dep.var.caption  = "")

```

#### Model 3 Regression {-} 

```{r}
lm_corn_rr <- lm(y2 ~ 0 + rr_corn + rr_rice  + region, # rc_corn + rc_rice + rc_soy + 
              data = regdat %>% filter(crop == "corn"))

lm_rice_rr <- lm(y2 ~ 0 + rr_corn + rr_rice  + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_rr <- lm(y2 ~ 0 +  rr_corn + rr_rice  +  region,
              data = regdat %>% filter(crop == "soybean"))

stargazer(lm_corn_rr, lm_rice_rr, lm_soy_rr, title = "Model 3 Results",column.labels = c("Corn", "Rice", "Soybean"), type = "text", digit = 3, dep.var.caption  = "")

```



### Model 4 {-}

use the last year's true profit 

```{r}
lm_corn_pftr <- lm(y2 ~ 0 + pftr_corn + pftr_rice + pftr_soy + region,
              data = regdat %>% filter(crop == "corn"))

lm_rice_pftr <- lm(y2 ~ 0 + pftr_corn + pftr_rice + pftr_soy + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_pftr <- lm(y2 ~ 0 + pftr_corn + pftr_rice + pftr_soy +  region,
              data = regdat %>% filter(crop == "soybean"))


stargazer(lm_corn_pftr, lm_rice_pftr, lm_soy_pftr, title = "Model 4 Results",column.labels = c("Corn", "Rice", "Soybean"), type = "text", digit = 3, dep.var.caption  = "")

```

### Model 5 {-}
```{r}
lm_corn_rr2 <- lm(y2 ~ 0 + rr_corn2 + rr_soy2  + region, # rc_corn + rc_rice + rc_soy + 
              data = regdat %>% filter(crop == "corn"))

lm_rice_rr2 <- lm(y2 ~ 0 + rr_corn2 + rr_soy2  + region,
              data = regdat %>% filter(crop == "rice"))

lm_soy_rr2 <- lm(y2 ~ 0 +  rr_corn2 + rr_soy2  +  region,
              data = regdat %>% filter(crop == "soybean"))

stargazer(lm_corn_rr2, lm_rice_rr2, lm_soy_rr2, title = "Model 5 Results",column.labels = c("Corn", "Rice", "Soybean"), type = "text", digit = 3, dep.var.caption  = "")
```



#### Prediction Results {-}

```{r echo = F}
pd_corn_pf <- predict(lm_corn_pf, newdata = preddat %>% filter(crop == "corn"))
pd_rice_pf <- predict(lm_rice_pf, newdata = preddat %>% filter(crop == "rice"))
pd_soy_pf <- predict(lm_soy_pf, newdata = preddat %>% filter(crop == "soybean"))

y_pred_pf <- rbind(pd_corn_pf, pd_rice_pf, pd_soy_pf)

share_est_pf <- round(sweep(exp(y_pred_pf), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_pf)) + 1) * 100, 2)


pd_corn_rev <- predict(lm_corn_rev, newdata = preddat %>% filter(crop == "corn"))
pd_rice_rev <- predict(lm_rice_rev, newdata = preddat %>% filter(crop == "rice"))
pd_soy_rev <- predict(lm_soy_rev, newdata = preddat %>% filter(crop == "soybean"))

y_pred_rev <- rbind(pd_corn_rev, pd_rice_rev, pd_soy_rev)

share_est_rev <- round(sweep(exp(y_pred_rev), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_rev)) + 1) * 100, 2)



pd_corn_rr<- predict(lm_corn_rr, newdata = preddat %>% filter(crop == "corn"))
pd_rice_rr <- predict(lm_rice_rr, newdata = preddat %>% filter(crop == "rice"))
pd_soy_rr <- predict(lm_soy_rr, newdata = preddat %>% filter(crop == "soybean"))

y_pred_rr <- rbind(pd_corn_rr, pd_rice_rr, pd_soy_rr)

share_est_rr <- round(sweep(exp(y_pred_rr), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_rr)) + 1) * 100, 2)

#model 5
pd_corn_rr2 <- predict(lm_corn_rr2, newdata = preddat %>% filter(crop == "corn"))
pd_rice_rr2 <- predict(lm_rice_rr2, newdata = preddat %>% filter(crop == "rice"))
pd_soy_rr2 <- predict(lm_soy_rr2, newdata = preddat %>% filter(crop == "soybean"))

y_pred_rr2 <- rbind(pd_corn_rr2, pd_rice_rr2, pd_soy_rr2)

share_est_rr2 <- round(sweep(exp(y_pred_rr2), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_rr2)) + 1) * 100, 2)


pd_corn_pftr <- predict(lm_corn_pftr, newdata = preddat %>% filter(crop == "corn"))
pd_rice_pftr <- predict(lm_rice_pftr, newdata = preddat %>% filter(crop == "rice"))
pd_soy_pftr <- predict(lm_soy_pftr, newdata = preddat %>% filter(crop == "soybean"))

y_pred_pftr <- rbind(pd_corn_pftr, pd_rice_pftr, pd_soy_pftr)

share_est_pftr <- round(sweep(exp(y_pred_pftr), MARGIN = 2, FUN = "/", STATS = colSums(exp(y_pred_pftr)) + 1) * 100, 2)

```

True Result in 2021

```{r}
share_true %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```

Model 1 Prediction

```{r}
share_est_pf %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```

Model 2 Prediction

```{r}
share_est_rev %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```

Model 3 Prediction

```{r}
share_est_rr %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```

Model 4 Prediction

```{r}
share_est_pftr %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```

Model 5 prediction

```{r}
share_est_rr2 %>% data.frame() %>% "colnames<-"(unique(regdat$region)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```


#### MSE Results {-}

```{r}
MSE1 <- rowMeans((share_true - share_est_pf)^2)
MSE2 <- rowMeans((share_true - share_est_rev)^2)
MSE3 <- rowMeans((share_true - share_est_rr)^2)
MSE4 <- rowMeans((share_true - share_est_pftr)^2)
MSE5 <- rowMeans((share_true - share_est_rr2)^2)

cbind(MSE1, MSE2, MSE3, MSE4, MSE5) %>% "colnames<-"(paste0("Model", 1:5)) %>% 
  "rownames<-"(unique(regdat$crop)[-4]) %>% pander::pander() 
```

